Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model \\ {\large \url{https://github.com/maxitg/GammaRays}}

### 2014-08-26 Paper/gammaRays.tex
Added open source notes to title and abstract

\title{Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model}
\author{
	Maxim S. Piskunov$^{1}$\thanks{\href{mailto:maxit@ms2.inr.ac.ru}{maxit@ms2.inr.ac.ru}} and
	Grigory I. Rubtsov$^{1}$\thanks{\href{mailto:grisha@ms2.inr.ac.ru}{grisha@ms2.inr.ac.ru}} \\
	$^{1}$Institute for Nuclear Research RAS, 117312, Moscow, Russia\\
}

\begin{document}
\maketitle

@@

	We suggest a simple geometrical model to explain this result.
	The main assumption is the jet opening angle dependence on radiation energy -- the most energetic photons are emitted near the axis of the jet.
	We also assume that all bursts are the same in their rest frames (that is their light curves differ only because of different redshifts and different view directions).
	To test this model, we compute the total energy of the burst, and confirm that it is below the constraint.
	We also compute the fraction of observable bursts in $(\unit[100]{MeV}, \unit[1]{GeV})$ band, which can also be observed in higher energies.
	This fraction matches the observations.
	We predict the distribution of observable stretching factors, which may be tested in the future when more observational data become available.
	Finally, we propose a way to estimate observer's off-axis angles (view directions) based on stretching factors and fractions of high energy photons.
\end{abstract}

>>>>

\title{
	Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model \\
	{\large \url{https://github.com/maxitg/GammaRays}}
}

\author{
	Maxim S. Piskunov$^{1}$\thanks{\href{mailto:maxit@ms2.inr.ac.ru}{maxit@ms2.inr.ac.ru}} and
	Grigory I. Rubtsov$^{1}$\thanks{\href{mailto:grisha@ms2.inr.ac.ru}{grisha@ms2.inr.ac.ru}} \\
	$^{1}$Institute for Nuclear Research RAS, 117312, Moscow, Russia\\
}

\begin{document}

\maketitle

@@

	We suggest a simple geometrical model to explain this result.
	The main assumption is the jet opening angle dependence on radiation energy -- the most energetic photons are emitted near the axis of the jet.
	We also assume that all bursts are the same in their rest frames (that is their light curves differ only because of different redshifts and different view directions).
	To test this model, we compute the total energy of the burst, and confirm that it is below the constraint.
	We also compute the fraction of observable bursts in $(\unit[100]{MeV}, \unit[1]{GeV})$ band, which can also be observed in higher energies.
	This fraction matches the observations.
	We predict the distribution of observable stretching factors, which may be tested in the future when more observational data become available.
	Finally, we propose a way to estimate observer's off-axis angles (view directions) based on stretching factors and fractions of high energy photons.

	All our code is open source, and is available freely on GitHub for you to download and play with.
\end{abstract}
